Analysis: NAME

### 2021-07-26 gc_fid_data.Rmd
attempting to collapse Fx

# set global chunk options for figure output
figure_prefix <- "PREFIX-"
knitr::opts_chunk$set(
  dev=c("png", "pdf"), dev.args=list(pdf = list(encoding="WinAnsi", useDingbats=FALSE)),
  fig.keep="all", fig.path=file.path("figures", figure_prefix))
```

@@

```{r}
root <- "data/gc_fid_data_2020/"
file_list = list.files(path = root)
all_data <-
  tibble(
    sample = file_list,
    file = file_list,
    data = map(file.path(root, file), read_chromeleon_export),
    injection_details = map(data, "injection_details"),
    integration_results = map(data, "integration_results")
  ) %>% select(-data)
```

@@

# Analyze data

@@

results %>% 
  filter(!str_detect(`Peak Name`, fixed("?"))) %>% 
  ggplot() +
  aes(`Peak Name`, `Relative Area`) +
  geom_bar(stat = "identity") +
  theme_figure(axis_x_rotate = 90) +
  scale_y_continuous(expand = c(0,0)) +
  facet_wrap(~sample)
```

```{r}
results %>% 
  ggplot() +
  aes(`Retention Time`, `Relative Height`, fill = `Peak Name`) +
  geom_bar(stat = "identity")
```

```{r}
results %>% 
  ggplot() +
  aes(`Retention Time`, `Relative Height`, fill = group, label = `Peak Name`) +
  geom_bar(stat = "identity") +
  facet_grid(sample ~ .) +
  theme_figure(legend = TRUE) +
  scale_y_continuous(expand = c(0, 0))
```

```{r}
library(plotly)
ggplotly(ggplot2::last_plot(), dynamicTicks = TRUE)
```

@@

```{r}
results %>% 
  filter(sample == "a") %>% 
  mutate(rt = `Retention Time` * 60) %>% 
  select(group, `Peak Name`, rt, rel_height = `Relative Height`) %>% 
  mutate(rt = round(rt, 1), rel_height = round(rel_height, 2)) %>%
  filter(rel_height > 1) %>% 
  openxlsx::write.xlsx(file.path("tables", "tsq_single_sample_peak_table.xlsx"))
```

>>>>

# set global chunk options for figure output
figure_prefix <- "PREFIX-"
knitr::opts_chunk$set(
  dev=c("png", "pdf"), dev.args=list(pdf = list(encoding="WinAnsi", useDingbats=FALSE)),
  fig.keep="all", fig.path=file.path("figures", figure_prefix))

# Define a way to negate  %in%
`%nin%` = Negate(`%in%`)
```

@@

```{r}
root <- "data/gc_fid_data_2020/"
file_list = list.files(path = root)
file_list <- file_list %>% 
  str_subset("blank", negate = TRUE) %>% 
  str_subset("Blank", negate = TRUE) %>% 
  str_subset("GCMS-STD", negate = TRUE) %>% 
  str_subset("BLK", negate = TRUE) # remove procedural blanks
sample_names <- file_list %>% 
  str_replace("FID.....", "") %>% 
  str_replace("_100ul-nhex.xls", "") %>% 
  str_replace("_100ul.xls", "")

all_data <-
  tibble(
    sample = sample_names,
    file = file_list,
    data = map(file.path(root, file), read_chromeleon_export),
    injection_details = map(data, "injection_details"),
    integration_results = map(data, "integration_results")
  ) %>% select(-data)
```

@@

# Tidy Data

## Unnest integrationd etails

@@

```

## Recombine Fractions for m0f0 + m0f3 samples
See `https://docs.google.com/document/d/1kBNM27kpLauVsBvefoXglYV64GAE0KPrE9SXfRSTvno/edit?usp=sharing` entry `6/8/2021` for more details.

```{r}
# Recombine Fractions for m0f0 + m0f3 samples
results_m0f0_m0f3 <- results %>% 
  filter(str_detect(sample, "_F")) %>% 
  mutate(frac = case_when(
    str_detect(sample, "F1") ~ "F1",
    str_detect(sample, "F2") ~ "F2",
    str_detect(sample, "F3") ~ "F3")) %>% 
  mutate(
    sample = str_remove(sample, "_F.")) %>% 
  mutate(
    sample = str_remove(sample, "_"))

```

```{r}
# Combine triplicate samples into one
results_trip <- results %>% 
  # Remove standards and fractions for this
  filter(sample != "FAME37.1") %>% 
  filter(sample != "TCBAME-2") %>% 
  filter(!str_detect(sample, "F1")) %>% 
  filter(!str_detect(sample, "F2")) %>% 
  filter(!str_detect(sample, "F3")) %>% 
  filter(!str_detect(sample, "cr")) %>%
  mutate(sample_rep = str_remove(sample, "[xyz]")) %>% 
  group_by(sample_rep, `Peak Name`) %>%
  # Replace NA Height and Area values with Zero in order to do summarizing operations
  mutate(`Relative Height` = replace(`Relative Height`, is.na(`Relative Height`), 0)) %>%
  mutate(`Relative Area` = replace(`Relative Area`, is.na(`Relative Area`), 0)) %>% 
  # Generate summary stats
  summarize(rel_area_max = max(`Relative Area`),
            rel_area_min = min(`Relative Area`),
            rel_height_max = max(`Relative Height`),
            rel_height_min = min(`Relative Height`),
            `Retention Time` = mean(`Retention Time`),
            `Relative Area` = mean(`Relative Area`),
            `Relative Height` = mean(`Relative Height`)) %>% 
  # Add some basic metadata
  mutate(inc_time = case_when(
    str_detect(sample_rep, "...0") ~ 0,
    str_detect(sample_rep, "...3") ~ 3,
    str_detect(sample_rep, "...7") ~ 7),
    site = case_when(
      str_detect(sample_rep, "c") ~ "GG Conifer",
      str_detect(sample_rep, "t") ~ "NWT Tundra",
      str_detect(sample_rep, "g") ~ "MM Grassland",
      str_detect(sample_rep, "m") ~ "GG Meadow")
  )
```

# Summary Plots
```{r}
p_0hr_FAs <- results_trip %>% filter(inc_time == "0") %>% 
  # Remove Standard Peaks
  filter(`Peak Name` %nin% c("PAIBE", "21:0 (STD)", "23:0 (STD)")) %>% 
  ggplot(aes(x = `Retention Time`, 
             y = `Relative Area`, 
             color = sample_rep, 
             fill = sample_rep, 
             label = `Peak Name`)) +
  geom_col(width = 0.08) +
  geom_errorbar(aes(ymin=rel_area_min, 
                    ymax = rel_area_max), 
                color = "black", 
                width = 0.05) +
  facet_wrap(~sample_rep, 
             ncol = 1, 
             scales = "free_y") +
  geom_label_repel(fill = "black", color = "white", alpha = 0.7, size = 3, nudge_y = 2, segment.color = "black") +
  ggtitle("PLFA Profile: 0hr") +
  theme_bw() +
  scale_color_jama() +
  scale_fill_jama()

p_72hr_FAs <- results_trip %>% filter(inc_time == "3") %>% 
  # Remove Standard Peaks
  filter(`Peak Name` %nin% c("PAIBE", "21:0 (STD)", "23:0 (STD)")) %>% 
  ggplot(aes(x = `Retention Time`, 
             y = `Relative Area`, 
             color = sample_rep, 
             fill = sample_rep, 
             label = `Peak Name`)) +
  geom_col(width = 0.08) +
  geom_errorbar(aes(ymin=rel_area_min, 
                    ymax = rel_area_max), 
                color = "black", 
                width = 0.05) +
  facet_wrap(~sample_rep, 
             ncol = 1, 
             scales = "free_y") +
  geom_label_repel(fill = "black", color = "white", alpha = 0.7, size = 3, nudge_y = 2, segment.color = "black") +
  ggtitle("PLFA Profile: 72hr") +
  theme_bw() +
  scale_color_jama() +
  scale_fill_jama()

p_168hr_FAs <- results_trip %>% filter(inc_time == "7") %>% 
  # Remove Standard Peaks
  filter(`Peak Name` %nin% c("PAIBE", "21:0 (STD)", "23:0 (STD)")) %>% 
  ggplot(aes(x = `Retention Time`, 
             y = `Relative Area`, 
             color = sample_rep, 
             fill = sample_rep, 
             label = `Peak Name`)) +
  geom_col(width = 0.08) +
  geom_errorbar(aes(ymin=rel_area_min, 
                    ymax = rel_area_max), 
                color = "black", 
                width = 0.05) +
  facet_wrap(~sample_rep, 
             ncol = 1, 
             scales = "free_y") +
  geom_label_repel(fill = "black", color = "white", alpha = 0.7, size = 3, nudge_y = 2, segment.color = "black") +
  ggtitle("PLFA Profile: 168hr") +
  theme_bw() +
  scale_color_jama() +
  scale_fill_jama()
p_168hr_FAs

```

## Biocrust Plots
```{r}
# Subsetting Intact Biocrust Experiment
results_cr <- results %>% filter(sample %in% c("cri0", "cri3", "cri5", "cri7"))
results_cr <- as.data.frame(results_cr)

results_cr <- results_cr %>% 
  # Add some basic metadata
  mutate(inc_time = case_when(
    str_detect(sample, "...0") ~ 0,
    str_detect(sample, "...3") ~ 3,
    str_detect(sample, "...5") ~ 5,
    str_detect(sample, "...7") ~ 7),
    site = "intact biocrust")
write.csv(file = "data/intact_biocrust_PLFAs.csv", results_cr)
```

```{r}
# Plot the intact biocrust PLFA profiles
p_cri_FAs <- results_cr %>% 
  # Remove Standard Peaks
  filter(`Peak Name` %nin% c("PAIBE", "21:0 (STD)", "23:0 (STD)")) %>% 
  ggplot(aes(x = `Retention Time`, 
             y = `Relative Area`, 
             color = sample, 
             fill = sample, 
             label = `Peak Name`)) +
  geom_col(width = 0.08) +
  facet_wrap(~sample, 
             ncol = 1, 
             scales = "free_y") +
  geom_label_repel(fill = "black", color = "white", alpha = 0.7, size = 2.5, nudge_y = 2, segment.color = "black") +
  theme_bw() +
  scale_color_jama() +
  scale_fill_jama()
p_cri_FAs

```

@@

```{r}
results %>% 
  filter(sample == "a") %>% 
  mutate(rt = `Retention Time` * 60) %>% 
  select(group, `Peak Name`, rt, rel_height = `Relative Height`) %>% 
  mutate(rt = round(rt, 1), rel_height = round(rel_height, 2)) %>%
  filter(rel_height > 1) %>% 
  openxlsx::write.xlsx(file.path("tables", "fid_single_sample_peak_table.xlsx"))
```
